### 2015-02-13 paper_20_sdo.tex
working on availability

    \item[App] (Application) - a software system or a collection of other apps, item[Project] - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
    \item[Release] - A collection of projects being put in production on a specified date
    \item[SIT]   (Systems Integration Testing) - The initial step of testing
        after the development phase of the SDLC.  This is typically 
        performed by members of the SDO.  It is validation that all the
        software components function together as expected.
    \item[UAT]   (User Acceptance Testing) - The final step of testing
        when a select few members of the user group are invited to
        validate the software system. Once validation has occured for
        UAT, the software system is ready to proceed to production
    \item[PROD]  (Production) - The software has been released to the final audience.
    \item[defect] ``A software defect is a bug or error that causes
                software to either stop operating or to produce
                invalid or unacceptable results'' as quoted from
            \cite{Jones2009}.  It is important to mention that even though defects are typically 
            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.

>>>>

    \item[App] (Application) - a software system or a collection of other applications 
    \item[Project] - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
    \item[Release] - A collection of projects being put in production on a specified date
    \item[SIT]   (Systems Integration Testing) - The initial step of testing
        after the development phase of the SDLC.  This is typically 
        performed by members of the SDO.  It is validation that all the
        software components function together as expected.
    \item[UAT]   (User Acceptance Testing) - The final step of testing
        when a select few members of the user group are invited to
        validate the software system. Once validation has occured for
        UAT, the software system is ready to proceed to production
    \item[PROD]  (Production) - The software has been released to the final audience.
    \item[defect] ``A software defect is a bug or error that causes
                software to either stop operating or to produce
                invalid or unacceptable results'' as quoted from
            \cite{Jones2009}.  It is important to mention that even though defects are typically 
            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.

### 2015-02-13 paper_40_mpi.tex
working on availability

            Special Note: The System ID for availability does not have to be the same
            as the Application ID for quality or any of the other elements.  Some 
            organizations have a one-to-one mapping between Applications being developed
            and systems being deployed.  Others have more complex sceranios that require
            multiple applications to be combined to form a system.  Then the availability
            of the system is tracked.

@@

                    System ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Uptime & Float & Optional \\
                    \myrowcolour%
                    Scheduled Downtime & Float & Optional \\
                    Unscheduled Downtime & Float  & Optional \\
                    \myrowcolour%
                    Percent Uptime & Float & Required \\
                    Expected Percent Uptime & Float & Required \\

@@

        \subsubsection{SATISFACTION}
            The satisfaction of the customer is also very important.  
            The following is an algorithm to calculate the satisfaction of software.
            \[
                S_2 = \frac{\sum^n_{i=1}\left( \frac{\sum^m_{j=1}a_{ij}- \frac{min + max}{2}}{m}  \right)}{n}
            \]

@@

            Question ID & String  & Required \\
            \myrowcolour%
            Question Text & String  & Optional \\
            Application ID & String & Required \\
            \myrowcolour%
            Frequency Date & Date & Required \\
            Response & Integer between min and max  & Required \\
            \myrowcolour%
            Response Date & Date & Optional \\

@@

>>>>

            Special Note: The Service ID for availability does not have to be the same
            as the Application ID for quality or any of the other elements.  Some 
            organizations have a one-to-one mapping between Applications being developed
            and services being deployed.  Others have more complex sceranios that require
            multiple applications to be combined to form a service.  Then the availability
            of the system is tracked.

@@

                    Service ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Uptime & Float & Optional \\
                    \myrowcolour%
                    Scheduled Downtime & Float & Optional \\
                    Unscheduled Downtime & Float  & Optional \\
                    \myrowcolour%
                    Percent Uptime & Float & Required \\
                    Expected Percent Uptime & Float & Required \\

@@

        \subsubsection{SATISFACTION}
            The satisfaction of users, customers, and/or business partners is 
            the third element to be measured.  This element is important because 
            in an established business, retaining customers is less expensive
            than actracting new customers \cite{Aulet2013}.  
            Depending upon the type of SDO,
            the customers may be internal or external to the organization.
            If one element of MPI was to be rated as the most important, satisfaction
            would be it.  Without satisfied customers, the rest of the measures do not matter.
            For example, having a quality
            application that is always available does not matter if it is not what the customer
            wants.  Surveys are used to measure satisfaction for MPI.

            \paragraph{SURVEYS}
                Write possible survey questions here.
                and explain the issues with surveys, see qualifier

            The questions  are answered on a scale of 1 to 5 with 1 being 
            \textbf{Strongly Misses Expectations} and 5 being \textbf{Strongly Exceeds
            Expectations}.

            \paragraph{SATISFACTION DATA}
                \begin{longtable}{@{}l rr rr}
                    \toprule%
                     \centering%
                     {\bfseries Column Name}
                     & {\bfseries Data Type}
                     &  \\

@@

                    Question ID & String  & Required \\
                    \myrowcolour%
                    Question Text & String  & Optional \\
                    Respondent ID & String & Optional \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Response & Integer & Required \\
                    \myrowcolour%
                    Response Date & Date & Optional \\
                    Application ID & String & Optional \\

@@

            \paragraph{SATISFACTION FORMULA}

            The following is an algorithm to calculate the satisfaction of software.
            \[
                S_2 = \frac{\sum^n_{i=1}\left( \frac{\sum^m_{j=1}a_{ij}- \frac{min + max}{2}}{m}  \right)}{n}
            \]
